\textbf{\sc Towards Deliberative Control of Autonomous Robots}

### 2012-02-06 europa-basics.tex
cpl of changes to CP section.

A set of constraints and variables that describe a problem domain are
typically represented as a Constraint Network, where the variables are
nodes and constraints are arcs between the variables. Having this
network representation in mind, Arc Consistency \comment{needs a
  definition} for a pair of variables $x,y$ is achieved if for every
value in $x$'s domain, there is a value in $y$'s domain that is
consistent with all the constraints that connect $x$ and $y$.  A naive
approach to ensuring arc consistency consists of cycling through all
the variable pairs and performing constraint propagation until there
are no variable domain changes. The AC-3 algorithm \cite{mackworth77},
a popular implementation, improves over the naive approach by ignoring
constraints whose variables were not affected since the last
iteration.

Arc Consistency and other sophisticated consistency algorithms can be
used to efficiently prove that a CP problem is unsatisfiable. However,
they generally cannot prove that a CP problem is satisfiable and
provide specific variable assignments that constitute solutions. For
that, search algorithms like global backtracking \comment{citation
  needed} or local search are used; these use consistency as an
efficient way to prune the search space \comment {citation CP
  Handbook}. In theory, solving a CP problem is NP-Hard
\cite{ghallab04}, but often very efficient in practice using a number
of consistency and search algorithms that are well understood.

CP is usually implemented as part of a programming language and
constraints are usually represented as objects \cite{puget95}. Any
constraint can be introduced and, as long as the constraint
propagation protocols specified by the hostCP system are enforced, it
will be indistinguishable from any other ``primitive'' CP constraint,
such as $\leq$ or $\geq$.

>>>>

A set of constraints and variables that describe a problem domain are
typically represented as a Constraint Network, where the variables are
nodes and constraints are arcs between the variables. Having this
network representation in mind, a pair of variables $x,y$ is said to be arc consistent if for every
value in $x$'s domain, there is a value in $y$'s domain that is
consistent with all the constraints that connect $x$ and $y$.  A naive
approach to ensuring arc consistency consists of cycling through all
the variable pairs and performing constraint propagation until there
are no variable domain changes. The AC-3 algorithm \cite{mackworth77},
a popular implementation, improves over the naive approach by ignoring
constraints whose variables were not affected since the last
iteration.

Arc Consistency and other, more stringent consistency definitions can be
used to efficiently prove that a CP problem is unsatisfiable. However,
they generally cannot prove that a CP problem is satisfiable and
provide specific variable assignments that constitute solutions. For
that, search algorithms like global backtracking \comment{citation
  needed} or local search are used; these use consistency as an
efficient way to prune the search space \comment {citation CP
  Handbook}. In theory, solving a CP problem is NP-Hard
\cite{ghallab04}, but often very efficient in practice using a number
of consistency and search algorithms that are well understood.

CP is usually implemented as part of a programming language and
constraints are usually represented as objects \cite{puget95}. Any
constraint that the user is able to reason about can be introduced into the system and, as long as the constraint
propagation protocols specified by the host CP system are enforced, it
will be indistinguishable from any other "primitive'' CP constraint,
such as $\leq$ or $\geq$.
